Open Split Tests

### 2021-06-10 inst/rmd/opensplittests.Rmd
Finish sample data.

```{r}
carb_data <- tribble(~name, ~rec_num, ~carbonate_mass, ~helium_added,
                     "C-1_1", 83028, 8.29,
                     "C-1_2", 83028, 9.01,
                     "C-1_3", 83028, 9.00,
                     "C-2_1", 1082, 8.23,
                     "C-2_2", 1082, 8.77,
                     "C-2_3", 1082, 7.34,
                     "NOSAMS-2_1", 38809, 7.72,
                     "NOSAMS-2_2", 38809, 7.69,
                     "NOSAMS-2_3", 38809, 8.86,
                     )

@@

@@

>>>>

```{r}
carb_data <- tribble(~name,         ~rec_num, ~carbonate_mass, ~helium_added,
                     "C-1_1",       83028,    8.29,            5,
                     "C-1_2",       83028,    9.01,            5,
                     "C-1_3",       83028,    9.00,            5,
                     "C-2_1",        1082,    8.23,            5,
                     "C-2_2",        1082,    8.77,            5,
                     "C-2_3",        1082,    7.34,            5,
                     "NOSAMS-2_1",  38809,    7.72,            5,
                     "NOSAMS-2_2",  38809,    7.69,            5,
                     "NOSAMS-2_3",  38809,    8.86,            5
                     )

@@

```{r}
df_sum %>% 
  plot_hgis_summary()
```

@@

```{r}
cons <- df_sum %>% 
  filter(as.numeric(Pos) > 4,
         !is.na(fm_consensus)) %>% 
  select(Sample.Name, fm_consensus, fm_corr, sig_fm_corr) %>% 
  mutate(Fm_diff = fm_corr - fm_consensus,
         sigma = amstools::sigma(fm_corr, fm_consensus, sig_fm_corr)) %>% 
  arrange(Sample.Name)

knitr::kable(cons)
```
